---
title: "Data Preparation and Feature Selection - Cycle 04"
author: "Cleverson Oliveira"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    highlight: textmate
    logo: logo.png
    theme: jou
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
    df_print: paged
    code_folding: hide
  pdf_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Imports

```{r, echo=FALSE}
#install.packages("devtools")
#devtools::install_github("ropensci/skimr")
#install.packages("gtsummary")
#install.packages("magick")
#install.packages("summarytools")
#install.packages("knitr")
#install.packages("kableExtra")
#devtools::install_github("kupietz/kableExtra")
#install.packages("gridExtra")
#install.packages("reshape2")
#install.packages("tidymodels")
#install.packages("randomForest")
#install.packages("tidyverse")
#install.packages("RcppEigen")
#install.packages("ranger")
#install.packages("xgboost")
#install.packages("kknn")
```

```{r, echo=FALSE}
library(dplyr)
library(tidyverse)
library(janitor)
library(gtsummary)
library(summarytools)
library(knitr)
library(kableExtra)
library(gridExtra)
library(readr)
library(ggplot2)
library(tidymodels)
library(randomForest)
```

# Data Collection

```{r collection, echo=FALSE}
df4 <- readRDS("df3.rds")
View(df4)
glimpse(df4)
```

# Column Description

```{r, echo=FALSE}
variables <- df4 %>% names()
description <- c(
  "Corresponds to the record (row) number",
  "Unique ID for the customer",
  "The surname of a customer ",
  "The credit score of the customer",
  "Customer’s location",
  "Customer's gender",
  "Customer's age",
  "Number of years that the customer has been a client ",
  "Customer's balance",
  "Number of products that a customer has purchased",
  "Denotes whether or not a customer has a credit card",
  "Denotes if the customer is active or not",
  "Customer's salary",
  "Whether or not the customer left the bank",
  "Customer has complaint or not",
  "Score provided by the customer for their complaint resolution",
  "Type of card hold by the customer",
  "The points earned by the customer for using credit card"
)

df_description <- tibble(variables = variables,
                  description = description)

kable(df_description, format = "html") %>% 
kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

# Data Preparation

Frequency encoding for policy_sales_channel

Target encoding for gender e region_code

## Target encoding

```{r, echo=FALSE}
gender_encoder <- df4 %>% 
  mutate(exited_num = ifelse(exited == "yes", 1, 0)) %>%
  group_by(gender) %>% 
  summarise(gender_num = mean(exited_num, na.rm = TRUE))

geography_encoder <- df4 %>% 
  mutate(exited_num = ifelse(exited == "yes", 1, 0)) %>%
  group_by(geography) %>% 
  summarise(geography_num = mean(exited_num, na.rm = TRUE))

# save in RDS
saveRDS(gender_encoder, "gender_encoder.rds")
saveRDS(geography_encoder, "geography_encoder.rds")
```

## Ordinal Encoding

```{r}
encoding <- c("diamond" = 1, "gold" = 2, "silver" = 3, "platinum" = 4)

card_type_encoder <- df4 %>% 
  #group_by(card_type) %>% 
  distinct(card_type) %>% 
  mutate(card_type_num = encoding[match(card_type, names(encoding))])

saveRDS(card_type_encoder, "card_type_encoder.rds")
```

### Building Encoder Function

```{r, echo=FALSE}
encoder_function <- function(df){
  df %>% 
  # add the new encoded columns and delete the original column
  left_join(gender_encoder) %>% 
  select(-gender) %>% 
  rename(gender = gender_num) %>% #View()
    
  left_join(geography_encoder) %>% 
  select(-geography) %>% 
  rename(geography = geography_num) %>% #View()

  left_join(card_type_encoder) %>% 
  select(-card_type) %>% 
  rename(card_type = card_type_num) #View()
} 
```

```{r, echo=FALSE}
saveRDS(encoder_function, "encoder_function.rds")
```

## Splitting data into train and test

```{r, echo=FALSE}
#encoder_function <- readRDS("encoder_function.rds")
df_preprocessed <- encoder_function(df4)
df_preprocessed <- df_preprocessed[, !names(df_preprocessed) %in% c("surname", "row_number")]
```

```{r, echo=FALSE}
set.seed(123)

df_split <- df_preprocessed %>% 
  initial_split(prop = 0.75, strata = exited)

df_train <- df_split %>% 
  training()

df_test <- df_split %>% 
  testing()
```

### Check response proportions

```{r, echo=FALSE}
df_train %>% 
  select(exited) %>% 
  tbl_summary(type = list(exited ~ "categorical"))

df_test %>% 
  select(exited) %>% 
  tbl_summary(type = list(exited ~ "categorical"))
```

### Using tidymodels steps to continue the preprocessing

```{r, echo=FALSE}
df_recipe <- recipe(exited ~.,
       data = df_train) %>% 
  step_normalize(age, credit_score, point_earned) %>% 
  step_scale(estimated_salary, balance) %>% 
  step_dummy(all_nominal(), -all_outcomes())
```

### Applying the recipe

```{r, echo=FALSE}
df_train_prep <- df_recipe %>% 
  prep(df_train)

df_train_processed <- df_train_prep %>% 
  bake(df_train)

df4 <- df_train_prep %>% bake(df4)
```

```{r, echo=FALSE}
df_test_processed <- df_train_prep %>% 
  bake(df_test)
```

# Feature Selection

```{r, echo=FALSE}
predictors <- df_train_processed %>% 
  select(-customer_id, -exited)

target <- df_train_processed$exited
```

```{r, echo=FALSE}
start_time <- Sys.time()

rf_model <- randomForest(predictors, target, ntree = 10, importance = TRUE)

end_time <- Sys.time()

print(end_time - start_time)
```

### Show results

```{r, echo=FALSE}
importance(rf_model) %>% View()
```

```{r, echo=FALSE}
varImpPlot(rf_model)
```

In this first cycle we are going to select the ten most important variables according to the mean decrease gini

```{r, echo=FALSE}
importance(rf_model) %>% 
  as_tibble(rownames = "rowname") %>% 
  arrange(desc(MeanDecreaseGini)) %>%  # arrange the importance
  select(rowname) %>%  # select the names of columns
  slice(1:10) %>%  # get only the first seven
  pull()
```

```{r, echo=FALSE}
#Final dataset
selected_columns <- c(
  "customer_id",
  "complain_no",
  "age",
  "num_of_products",
  "balance",
  "geography",
  "is_active_member_no",
  "credit_score",
  "estimated_salary",
  "point_earned",
  "tenure",
  "exited"
)

df4 <- df4 %>% 
  select(all_of(selected_columns))

saveRDS(df4, "df4.rds")
```
